Causal Impact of Masks, Policies, Behavior on Early Covid-19 Pandemic in the U.S.

### 2020-09-18 tex/covidEffectOfNPI-revision.tex
Changed tex file to use the 'elsarticle' class.

\documentclass[11pt,reqno,letter]{amsart}
%\pdfoutput=1
\usepackage{amsmath}

@@

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[left=1.25in,right=1.25in,top=1.5in,bottom=1.25in]{geometry}
\usepackage{multirow}
\usepackage{verbatim}
\usepackage{float}
\usepackage{rotating}
%\usepackage{pxfonts}
%\usepackage{isomath}
%\usepackage{newpxtext}
%\usepackage{newpxmath}
\usepackage[dvipsnames]{xcolor}
\usepackage[normalem]{ulem}
\usepackage{booktabs}

@@

\usetikzlibrary{positioning}
\geometry{letterpaper}
%\usepackag\Ep[parfill]{parskip}    % Activate to begin paragraphs
%with an empty line rather than an indent

\setlength{\parskip}{.4cm}
\geometry{centering}
\usepackage{mathtools}

@@

\usepackage[authoryear]{natbib}
\usepackage{pdflscape}
\usepackage{afterpage}
\usepackage{capt-of}

@@

\title[Causal Impact of Masks, Policies, Behavior]
{Causal Impact of Masks, Policies, Behavior on Early Covid-19 Pandemic in the U.S.}\thanks{We are grateful to Daron Acemoglu, V.V. Chari, Raj Chetty,  Christian Hansen, Glenn Ellison, Ivan Fernandez-Val, David Green,  Ido Rosen, Konstantin Sonin, James Stock, Elie Tamer, and Ivan Werning for helpful comments. We also thank Chiyoung Ahn,
Joshua Catalano,  Jason Chau, Samuel Gyetvay, Sev Chenyu Hou,
Jordan Hutchings, and Dongxiao Zhang  for excellent research assistance.  We are especially grateful
to   C. Jessica E. Metcalf and an anonymous referee for detailed and insightful comments,
which considerable improved the paper. All mistakes are our own. }

\author{Victor Chernozhukov}
\address{Department of Economics and Center for Statistics and Data Science, MIT,  MA 02139}
\email{vchern@mit.edu}
%\urladdr{www.mit.edu/$\sim$vcherm} % Delete if not wanted.
\author{Hiroyuki Kasahara}
\address{ Vancouver School of Economics, UBC, 6000 Iona Drive, Vancouver, BC.}
\email{hkasahar@mail.ubc.ca}

\author{Paul Schrimpf}
\address{ Vancouver School of Economics, UBC, 6000 Iona Drive, Vancouver, BC.}
\email{schrimpf@mail.ubc.ca}

@@

\keywords{Covid-19, causal impact, masks, non-essential business, policies, behavior}

@@

\begin{figure}[ht]
  \caption{Case and death growth conditional on mask mandates \label{fig:masks}}\vspace{0.2cm}
 \begin{minipage}{\linewidth}
    \centering
    \begin{tabular}{cc}
      \includegraphics[width=0.5\textwidth]{tables_and_figures/pmaskbus-cases-14}
      &
        \includegraphics[width=0.5\textwidth]{tables_and_figures/pmaskbus-deaths-21}
    \end{tabular}
    \begin{flushleft}
      \scriptsize In these figures, red points are the case or death
      growth rate in states without a mask mandate. Blue points are
      states with a mask mandate 14 (21 for deaths) days prior. The
      red line is the average across states without a mask mandate 14
      (21 for deaths) days earlier. The blue line is the average
      across states with a mask mandate 14 (21 for deaths) earlier.
    \end{flushleft}
  \end{minipage}%\\ \medskip
% \begin{minipage}{\linewidth}
%    \centering
%    \begin{tabular}{cc}
%      \includegraphics[width=0.5\textwidth]{tables_and_figures/pmaskbus-cases-res-14}
%      &
%        \includegraphics[width=0.5\textwidth]{tables_and_figures/pmaskbus-deaths-res-21}
%    \end{tabular}
%    \begin{flushleft}
%      \scriptsize In these figures, red points are the regression residuals of case or death
%      growth rate on confounders in states without a mask mandate. Blue points are
%      states with a mask mandate 14 (21 for deaths) days prior. The
%      red line is the average across states without a mask mandate 14
%      (21 for deaths) days earlier. The blue line is the average
%      across states with a mask mandate 14 (21 for deaths) earlier.
%    \end{flushleft}
%  \end{minipage}
\end{figure}

@@

@@

>>>>

\documentclass[3p, longtitle]{elsarticle}
%\pdfoutput=1
\usepackage{amsmath}

@@

\usepackage{graphicx}
\usepackage{hyperref}
%\usepackage[left=1.25in,right=1.25in,top=1.5in,bottom=1.25in]{geometry}
\usepackage{multirow}
\usepackage{verbatim}
\usepackage{float}
\usepackage{rotating}
%\usepackage{pxfonts}
%\usepackage{isomath}
%\usepackage{newpxtext}
%\usepackage{newpxmath}
\usepackage[dvipsnames]{xcolor}
\usepackage[normalem]{ulem}
\usepackage{booktabs}

@@

\usetikzlibrary{positioning}
%\geometry{letterpaper}
%\usepackag\Ep[parfill]{parskip}    % Activate to begin paragraphs
%with an empty line rather than an indent

%\setlength{\parskip}{.4cm}
%\geometry{centering}
\usepackage{mathtools}

@@

%\usepackage[authoryear]{natbib}
\usepackage{pdflscape}
\usepackage{afterpage}
\usepackage{capt-of}

@@

%\title[Causal Impact of Masks, Policies, Behavior]{Causal Impact of Masks, Policies, Behavior on Early Covid-19 Pandemic in the U.S.}
\title{Causal Impact of Masks, Policies, Behavior on Early Covid-19
  Pandemic in the U.S.}

%% Formatting instructions move this to the end
% \thanks{We are grateful to Daron Acemoglu, V.V. Chari, Raj Chetty,  Christian Hansen, Glenn Ellison, Ivan Fernandez-Val, David Green,  Ido Rosen, Konstantin Sonin, James Stock, Elie Tamer, and Ivan Werning for helpful comments. We also thank Chiyoung Ahn,
% Joshua Catalano,  Jason Chau, Samuel Gyetvay, Sev Chenyu Hou,
% Jordan Hutchings, and Dongxiao Zhang  for excellent research assistance.  We are especially grateful
% to   C. Jessica E. Metcalf and an anonymous referee for detailed and insightful comments,
% which considerable improved the paper. All mistakes are our own. }

\author{Victor Chernozhukov}
\ead{vchern@mit.edu}
%\urladdr{www.mit.edu/$\sim$vchern} % Delete if not wanted.
\address{Department of Economics and Center for Statistics and Data
  Science, MIT,  MA 02139}

\author{Hiroyuki Kasahara \corref{cor1}}
\ead{hkasahar@mail.ubc.ca}
\address{Vancouver School of Economics, UBC, 6000 Iona Drive, Vancouver, BC.}
\author{Paul Schrimpf}
\ead{schrimpf@mail.ubc.ca}
\address{Vancouver School of Economics, UBC, 6000 Iona Drive, Vancouver, BC.}

\cortext[cor1]{Corresponding author}

@@

\begin{keyword}
  Covid-19, causal impact, masks, policies, behavior
\end{keyword}

@@

\clearpage
\begin{figure}[ht]
  \caption{Case and death growth conditional on mask mandates \label{fig:masks}}\vspace{0.2cm}
 \begin{minipage}{\linewidth}
    \centering
    \begin{tabular}{cc}
      \includegraphics[width=0.5\textwidth]{tables_and_figures/pmaskbus-cases-14}
      &
        \includegraphics[width=0.5\textwidth]{tables_and_figures/pmaskbus-deaths-21}
    \end{tabular}
    \begin{flushleft}
      \scriptsize In these figures, red points are the case or death
      growth rate in states without a mask mandate. Blue points are
      states with a mask mandate 14 (21 for deaths) days prior. The
      red line is the average across states without a mask mandate 14
      (21 for deaths) days earlier. The blue line is the average
      across states with a mask mandate 14 (21 for deaths) earlier.
    \end{flushleft}
  \end{minipage}%\\ \medskip
% \begin{minipage}{\linewidth}
%    \centering
%    \begin{tabular}{cc}
%      \includegraphics[width=0.5\textwidth]{tables_and_figures/pmaskbus-cases-res-14}
%      &
%        \includegraphics[width=0.5\textwidth]{tables_and_figures/pmaskbus-deaths-res-21}
%    \end{tabular}
%    \begin{flushleft}
%      \scriptsize In these figures, red points are the regression residuals of case or death
%      growth rate on confounders in states without a mask mandate. Blue points are
%      states with a mask mandate 14 (21 for deaths) days prior. The
%      red line is the average across states without a mask mandate 14
%      (21 for deaths) days earlier. The blue line is the average
%      across states with a mask mandate 14 (21 for deaths) earlier.
%    \end{flushleft}
%  \end{minipage}
\end{figure}

@@

\section*{Acknowledgements}

We are grateful to Daron Acemoglu, V.V. Chari, Raj Chetty, Christian
Hansen, Glenn Ellison, Ivan Fernandez-Val, David Green, Ido Rosen,
Konstantin Sonin, James Stock, Elie Tamer, and Ivan Werning for
helpful comments. We also thank Chiyoung Ahn, Joshua Catalano, Jason
Chau, Samuel Gyetvay, Sev Chenyu Hou, Jordan Hutchings, and Dongxiao
Zhang for excellent research assistance.  We are especially grateful
to C. Jessica E. Metcalf and an anonymous referee for detailed and
insightful comments, which considerable improved the paper. All
mistakes are our own.

@@

\section{Additional Results}
